Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-24 paper/main.tex
related work

Our approach shares the overall goal of spectrum-based fault localization:
pinpointing suspicious statements to reducing debugging effort. However,
where spectrum-based traditionally focus on larger, industrial-scale
programs, we target beginner-written software. Spectrum methods require
multiple test cases (ideally very many of them); we use just one program
execution. Spectrum methods focus heavily on dynamic features; we make
critical use of syntactic, contextual and type information as well.
In addition, some human studies have focused specifically on accuracy and
expertise for fault localization~\cite{fry2010,Prabhakararao03,ruthruff05};
our decision to use particular features to support beginning programmers is
informed by such insights.

@@

In the programming languages community, a large body of work has focused on
localizing faults and providing better error messages, typically through
the use of type information. \fixme{Sherrloc, Mycroft, Nate, etc.}

>>>>

Our approach shares the overall goal of spectrum-based fault localization:
pinpointing suspicious statements to reduce debugging effort. However,
where spectrum-based traditionally focus on larger, industrial-scale
programs, we target beginner-written software. Spectrum methods require
multiple test cases (ideally very many of them); we use just one program
execution. Spectrum methods focus heavily on dynamic features; we make
critical use of syntactic, contextual and type information as well.
In addition, some human studies have focused specifically on accuracy and
expertise for fault localization~\cite{fry2010,Prabhakararao03,ruthruff05};
our decision to use particular features to support beginning programmers is
informed by such insights.

@@

In the programming languages community, a large body of work has focused on
localizing faults and providing better error messages, typically through
the use of type information. SHErrLoc~\cite{SHErrLoc} identifies a set of
incompatible type constraints, then chooses the likely type error using the
Bayesian heuristic that the program is probably mostly correct. We rely on the
complementary heuristic that faults will share characteristics
with previously recorded faults, and apply this heuristic to features beyond
just type information. Mycroft~\cite{MYCROFT-type-errors} modifies existing
type inference algorithms to produce a ``correcting set'' for a program with
a type error. Mycroft assumes that the minimal such set is the most
desirable to the user, and has no way to rank multiple equally
small sets. We instead use machine learning to agree with human judgements.
NATE~\cite{learning-to-blame} uses machine learning on static and contextual
features, including static types, to localize type errors in OCaml
code. We employ a similar approach to localize Python faults, but we use
dynamic features as well as static and contextual ones, we handle a wide
variety of errors beyond type errors, and we evaluate our approach on a set of
programs both more heterogeneous and almost two orders of magnitude larger than
the NATE dataset.
